### 2004-07-01 doc/Simulation_and_Control_using_Supremica/automationobjects.tex
*** empty log message ***

Introduce Automation Objects
Define the different views (Model-View-Controller)
	Configuration
	Human-Machine Interface
	Control
	Simulation

>>>>

%Introduce Automation Objects

%% Why automation objects? Background.
Using only function blocks efficient hierarchical control
system design is very time consumig. To facilitate easier
and more rapid design process a new kind of design object
needs to be introduced. Before that the purpose of that kind
of object has to be defined.

%% Definition. Multi view objects where the view is the
%% interface exposed for different purposes.

% Define the different views (Model-View-Controller) if relevant.
%% Configuration
%% Human-Machine Interface
%% Control
%% Simulation

% Introduce the example

### 2004-07-01 doc/Simulation_and_Control_using_Supremica/functionblocks.tex
*** empty log message ***

\section{FBEditor}
Function Block Development Kit (FBDK) ~\cite{c:fun:2002} is a
software toolkit that enables users to build and test data types,
function block types, resource types, device types and system
configurations according to the IEC 61499 standard. FBEditor is a
part of the FBDK toolkit that provides a development and runtime
environment for applications based on the IEC 61499 standard.
Figure \ref{f:FBEditor} shows the editor being used to load a
function block used for controlling a motor.

%
%\singlespace
\begin{figure}
\begin{center}
\epsfig{file=images/functionblocks/FBEditor.eps, scale=.6}
\caption[FBEditor]{FBEditor{\protect ~\cite{c:fun:2002}}}
\label{f:FBEditor}
\end{center}
\end{figure}
%\doublespace
%

FBEditor enables the users to edit the block definitions through
both a text editor and through a graphical user interface. New
data types, basic function blocks, composite function blocks,
execution control charts and other higher level entities may be
created through the editor. The attributes of the blocks (data and
events) may also be examined through a graphical user interface.
The function blocks can be examined at the device level as shown
in Figure \ref{f:Editor-Devices} or at the level of individual
attributes like the connections, as shown in figure
\ref{f:Editor-Mapping}.

The editor supports the languages supported by the standard
(Structured text, execution control chart etc.). It uses XML as
the exchange format to ensure portability across various domains.
Figure \ref{f:Editor-Versions} shows how the editor can also be
used to manage meta properties like versions, owner entities,
authors etc.

%
%\singlespace
\begin{figure}
\begin{center}
\epsfig{file=images/functionblocks/Editor-Devices.eps, scale=.6} \caption[FBEditor
- Editing system devices]{FBEditor - Editing system
devices{\protect ~\cite{c:fun:2002}}} \label{f:Editor-Devices}
\end{center}
\end{figure}
%\doublespace
%

%
%\singlespace
\begin{figure}
\begin{center}
\epsfig{file=images/functionblocks/Editor-Mapping.eps, scale=.6} \caption[FBEditor
- Editing device connections]{FBEditor - Editing device
connections{\protect ~\cite{c:fun:2002}}} \label{f:Editor-Mapping}
\end{center}
\end{figure}
%\doublespace
%

%
%\singlespace
\begin{figure}
\begin{center}
\epsfig{file=images/functionblocks/Editor-Versions.eps, scale=.6}
\caption[FBEditor - Editing meta properties]{FBEditor - Editing
meta properties{\protect ~\cite{c:fun:2002}}}
\label{f:Editor-Versions}
\end{center}
\end{figure}
%\doublespace
%
FBEditor has a navigation pane that allows the user to choose the
display on the worksheet area, including the external interface;
the Execution Control Chart (ECC) for basic function block type;
service primitive sequences for service interface function block
types; and function block networks for composite function block
types, device and resource types and instances, and system
configurations. The worksheet / viewport area contains the
function block diagram for the currently selected instance.
Different components of the diagram can be dragged around for
better readability.

FBEditor has been developed in Java language. Hence in order to
run simulations on applications written using the editor, one
needs to generate the Java classes that correspond to the source
files for the function blocks written in structured text (for
instance). The editor has a code generation mechanism through
which it parses through the source files and generates a Java
class corresponding to each block.

On occurrence of certain input events, the user needs to specify
the algorithms that should be scheduled to be executed and the
output events that should signal the completion of algorithms.
This may be done either by editing the generated Java files or by
enclosing the algorithm inside especially marked tags in the
source files. The files are then compiled and simulations can be
run from within the editor environment. Figure
\ref{f:Editor-Transitions} shows the assignment of output events
on the transitions through the editing of the execution control
chart.

%
%\singlespace
\begin{figure}
\begin{center}
\epsfig{file=images/functionblocks/Editor-Transitions.eps, scale=.6}
\caption[FBEditor Editing the execution control chart]{FBEditor
Editing the execution control chart{\protect ~\cite{c:fun:2002}}}
\label{f:Editor-Transitions}
\end{center}
\end{figure}
%\doublespace
%

>>>>

% \section{FBEditor}
% Function Block Development Kit (FBDK) ~\cite{c:fun:2002} is a
% software toolkit that enables users to build and test data types,
% function block types, resource types, device types and system
% configurations according to the IEC 61499 standard. FBEditor is a
% part of the FBDK toolkit that provides a development and runtime
% environment for applications based on the IEC 61499 standard.
% Figure \ref{f:FBEditor} shows the editor being used to load a
% function block used for controlling a motor.

% %
% %\singlespace
% \begin{figure}
% \begin{center}
% \epsfig{file=images/functionblocks/FBEditor.eps, scale=.6}
% \caption[FBEditor]{FBEditor{\protect ~\cite{c:fun:2002}}}
% \label{f:FBEditor}
% \end{center}
% \end{figure}
% %\doublespace
% %

% FBEditor enables the users to edit the block definitions through
% both a text editor and through a graphical user interface. New
% data types, basic function blocks, composite function blocks,
% execution control charts and other higher level entities may be
% created through the editor. The attributes of the blocks (data and
% events) may also be examined through a graphical user interface.
% The function blocks can be examined at the device level as shown
% in Figure \ref{f:Editor-Devices} or at the level of individual
% attributes like the connections, as shown in figure
% \ref{f:Editor-Mapping}.

% The editor supports the languages supported by the standard
% (Structured text, execution control chart etc.). It uses XML as
% the exchange format to ensure portability across various domains.
% Figure \ref{f:Editor-Versions} shows how the editor can also be
% used to manage meta properties like versions, owner entities,
% authors etc.

% %
% %\singlespace
% \begin{figure}
% \begin{center}
% \epsfig{file=images/functionblocks/Editor-Devices.eps, scale=.6} \caption[FBEditor
% - Editing system devices]{FBEditor - Editing system
% devices{\protect ~\cite{c:fun:2002}}} \label{f:Editor-Devices}
% \end{center}
% \end{figure}
% %\doublespace
% %

% %
% %\singlespace
% \begin{figure}
% \begin{center}
% \epsfig{file=images/functionblocks/Editor-Mapping.eps, scale=.6} \caption[FBEditor
% - Editing device connections]{FBEditor - Editing device
% connections{\protect ~\cite{c:fun:2002}}} \label{f:Editor-Mapping}
% \end{center}
% \end{figure}
% %\doublespace
% %

% %
% %\singlespace
% \begin{figure}
% \begin{center}
% \epsfig{file=images/functionblocks/Editor-Versions.eps, scale=.6}
% \caption[FBEditor - Editing meta properties]{FBEditor - Editing
% meta properties{\protect ~\cite{c:fun:2002}}}
% \label{f:Editor-Versions}
% \end{center}
% \end{figure}
% %\doublespace
% %
% FBEditor has a navigation pane that allows the user to choose the
% display on the worksheet area, including the external interface;
% the Execution Control Chart (ECC) for basic function block type;
% service primitive sequences for service interface function block
% types; and function block networks for composite function block
% types, device and resource types and instances, and system
% configurations. The worksheet / viewport area contains the
% function block diagram for the currently selected instance.
% Different components of the diagram can be dragged around for
% better readability.

% FBEditor has been developed in Java language. Hence in order to
% run simulations on applications written using the editor, one
% needs to generate the Java classes that correspond to the source
% files for the function blocks written in structured text (for
% instance). The editor has a code generation mechanism through
% which it parses through the source files and generates a Java
% class corresponding to each block.

% On occurrence of certain input events, the user needs to specify
% the algorithms that should be scheduled to be executed and the
% output events that should signal the completion of algorithms.
% This may be done either by editing the generated Java files or by
% enclosing the algorithm inside especially marked tags in the
% source files. The files are then compiled and simulations can be
% run from within the editor environment. Figure
% \ref{f:Editor-Transitions} shows the assignment of output events
% on the transitions through the editing of the execution control
% chart.

% %
% %\singlespace
% \begin{figure}
% \begin{center}
% \epsfig{file=images/functionblocks/Editor-Transitions.eps, scale=.6}
% \caption[FBEditor Editing the execution control chart]{FBEditor
% Editing the execution control chart{\protect ~\cite{c:fun:2002}}}
% \label{f:Editor-Transitions}
% \end{center}
% \end{figure}

%\doublespace
%
